---
title: "NEON Data Institute Final Project"
author: "David McCaffrey and Enrique Monta&ntilde;o"
date: "June 23, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Individual Tree Crown and Species Identification using Spectrum and Water Indices

## Ojectives

Find sites with inventeries.  Find associated products.  Use CHM and crown metrics from individual trees.  This is where we expect to see trees.  Run ITC on 

Validated canopy and estimated canopy from inventories
estimated canopy from ITC, what error are we seeing between the two?

extract spectra from points
calculate or extract indices (ndvi, water stress)


Workflow:
* 


## Test of loading site inventory data 

```{r load-site-inventory}
source("scripts/load_data.R")

# site name
site <- "sjer"

inventory <- loadSiteData(site = site, type = "Struct")
inventory

# list of unique species at the site
site_species <- listSpecies(inventory)
site_species
length(site_species)


```

