---
title: "NEON Data Institute Final Project"
author: "David McCaffrey and Enrique Monta&ntilde;o"
date: "June 23, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Individual Tree Crown and Species Identification using Spectrum and Water Indices

## Ojectives

Find sites with inventeries.  Find associated products.  Use CHM and crown metrics from individual trees.  This is where we expect to see trees.  Run ITC on 

Validated canopy and estimated canopy from inventories
estimated canopy from ITC, what error are we seeing between the two?

extract spectra from points
calculate or extract indices (ndvi, water stress)


Workflow:
* 


## Test of loading site inventory data 

```{r load-site-inventory}
library(raster)
library(rgdal)
library(sp)
library(rgeos)
library(rhdf5)
library(neonAOP)
source("scripts/load_data.R")
source("scripts/neon-create-aop-subset-master/find-aopHSI-flightlines.R")
source("scripts/bufferPoints.R")

# site name
site <- "sjer"

inventory <- loadSiteData(site = site, type = "structure")
inventory

# list of unique species at the site
site_species <- listSpecies(inventory)
site_species
length(site_species)

# get list of flightlines
### SJER clip
site <- "SJER"
domain <- "D17"
fullDomain <- "D17-California"
year <- "2013"

##### Define your hard drive path. Mac's often use "volumes" for an external hard drive
##### Windows often use a letter "D:" etc
drivePath <- "Volumes"
driveName <- "AOP-NEON1-4"

########## Reflectance data variables based upon the hard drive structure
dataProduct <- "Reflectance"
dataType <- "Spectrometer"
level <- paste0(site,"_L1")
productType <- paste0(site,"_", dataType)



### Define the data directory where the h5 files are stored

dataDir <- file.path(drivePath, driveName,
                      domain,
                      site, year, level, productType, dataProduct)


# you only need this is you are using a mac
dataDir <- paste0("/", dataDir)
# get a list of all files in the dir
# if this variable returns no values, that means your dataDir is wrong OR
# the data dir doesn't have any information in it.
h5.files <- list.files(dataDir, pattern = '\\.h5$', full.names = TRUE)

ptShape <- readOGR("../NEONdata/D17-California/SJER/vector_data/", "SJER_plot_centroids")

# buffer the points to polygons with 20m radius
ptPoly <- bufferPoly(site, ptShape, 20)
  
goodFlightLines <-  find_intersect_h5(h5.files, ptPoly)
checkExtent




```

